\titel

### 2014-03-09 presentation/presa.tex
added ff planner and uncertainty

    \begin{itemize}
      \item From initial state to goal state?
      \item Create a planning plan.
    \end{itemize}

  \end{columns}

@@

\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown. Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence}

@@

Meet my plant

    \includegraphics[scale=0.08]{images/plant.jpg}
\end{frame}

@@

  \begin{columns}
    \column{0.3\textwidth}
    \includegraphics[width=\textwidth]{images/plant.jpg}

    \column{0.7\textwidth}
    How to plan when to water the plant?

    \begin{itemize}
      \item Uncertainty from Wind
      \item Sunlight
      \item Water
    \end{itemize}

  \vspace{1cm}
  What if picking up a block fails?

@@

@@

''We have presented an approach to domain independent planning that, \emph{at the time being}, outperforms all existing technology on the majority of the currently available benchmark domains.''

@@

Inspired by three new approaches in plan generation during that time:
	\begin{itemize}
		\item Planning graphs
		\begin{itemize}
			\item Nodes are actions and atomic facts arranged into alternate levels
			\item Edges from atomic facts to actions represents conditions
			\item Edges from actions to atomic facts represent true or false 
		\end{itemize}
		\item Planning as a satisfiability method
		\item Heuristic search planning approach
	\end{itemize}
\end{frame}

Relies on a 
	\begin{itemize}
		\item Forward state space search that combines hill-climbing and systematic search
		\item Heuristic estimating goal distances by ignoring delete lists - relaxed GRAPHPLAN
	\end{itemize}
\end{frame}

Insert image on search state, enforced hill climbing, call relaxed graphplan, inform search with goal distance estimate and maybe promising succesors, solution plan or fail, possible search from scratch using hast tabel with visited states 
\end{frame}

@@

To avoid wasting time in the presence of goal ordering:
	\begin{itemize}
		\item Goal deletion
		\item Goal agenda techniques
	\end{itemize}
\end{frame}

@@

Perks
	\begin{itemize}
		\item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
		\item Most domains in the IPCC are simple in their structure and can be easily solves using gree algorithms like FF
	\end{itemize}

@@

  \begin{itemize}
    \item In the ``Future Work'' the authors promised to generalize to Hybrid MDPs
    \item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
      \begin{itemize}
        \item Extends from discrete states to continues
        \item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
      \end{itemize}
  \end{itemize}

@@

@@

>>>>

    \begin{itemize}
      \item From initial state to goal state?
      \item Create a planning plan.
      \item Assumptions:
        \begin{itemize}
          \item Determinism
          \item Full observability
          \item Reachability goals
        \end{itemize}
    \end{itemize}
  \end{columns}

@@

  \emph{``Uncertainty applies to predictions of future events, to physical
  measurements that are already made, or to the unknown. Uncertainty arises in
  partially observable and/or stochastic environments, as well as due to
  ignorance and/or indolence''}

  \vspace{2cm}

  \tiny{http://en.wikipedia.org/wiki/Uncertainty}

@@

@@

  \begin{columns}
    \column{0.25\textwidth}
    \uncover<1> {Meet my plant}
    \includegraphics[width=\textwidth]{images/plant.jpg}

    \column{0.75\textwidth}
    \uncover<2->{%

      How to plan when to water the plant?

      \begin{itemize}
        \item Uncertainty from Wind
        \item Sunlight
        \item Water
      \end{itemize}
    }
  \end{columns}

  \vspace{1cm}
  \uncover<3-> {What if picking up a block fails?}

\begin{frame}
  \frametitle{Markov Decision Processes}

  \begin{itemize}
    \item Very much like a Classical Planner
    \item \alert{except} each action has a \alert{probability}
      \begin{itemize}
        \item \alert{Stochastic}
        \item Full observability
        \item Reachability goals
      \end{itemize}
    \item For example in the Blocksworld: The Pick Up action might fail.
  \end{itemize}

  \begin{columns}
    \column{0.8\textwidth}

    \begin{itemize}
      \item 1970s: STRIPS
      \item 1995: Graphplan
      \item 2000: FastForward (FF)
      \item 2004: FF-Replan
      \item 2010: RFF
      \item 2014:~?
    \end{itemize}

    \column{0.2\textwidth}
    \includegraphics[width=\textwidth]{images/shakey.png}

@@

  ``We have presented an approach to domain independent planning that, \emph{at
  the time being}, outperforms all existing technology on the majority of the
  currently available benchmark domains.''

@@

  Inspired by three new approaches in plan generation during that time:

  \begin{itemize}
    \item Planning graphs
    \begin{itemize}
      \item Nodes are actions and atomic facts arranged into alternate levels
      \item Edges from atomic facts to actions represents conditions
      \item Edges from actions to atomic facts represent true or false
    \end{itemize}
    \item Planning as a satisfiability method
    \item Heuristic search planning approach
  \end{itemize}
\end{frame}

  Relies on a

  \begin{itemize}
    \item Forward state space search that combines hill-climbing and systematic search
    \item Heuristic estimating goal distances by ignoring delete lists - relaxed GRAPHPLAN
  \end{itemize}

@@

  Insert image on search state, enforced hill climbing, call relaxed Graphplan,
  inform search with goal distance estimate and maybe promising successors,
  solution plan or fail, possible search from scratch using hast table with
  visited states

@@

  To avoid wasting time in the presence of goal ordering:

  \begin{itemize}
    \item Goal deletion
    \item Goal agenda techniques
  \end{itemize}

@@

  Perks
  \begin{itemize}
    \item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
    \item Most domains in the IPCC are simple in their structure and can be easily solves using greedy algorithms like FF
  \end{itemize}

@@

  \begin{itemize}
    \item In the ``Future Work'' the authors promised to generalize to Hybrid MDPs
  \end{itemize}

@@

\begin{frame}
  \frametitle{State-of-the-Art}

  \begin{itemize}
    \item \emph{``Probabilistic Planning via Determinization in Hindsight''} (2008) \\
      Improves FF-Replan with hindsight optimization.
    \item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
      \begin{itemize}
        \item Extends from discrete states to continues
        \item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
      \end{itemize}
    \item \emph{``Planning under partial observability by classical replanning: Theory and experiments''} (2011) \\
      Translates a POMDP to a classical planning problem where it can use \texttt{FF}.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Questions?}
\end{frame}
